SemanticPaint

### 2015-12-06 cv3d_seminar/paper.tex
results

\begin{table}[!ht]	
 \center
 \caption{Comparison of VOP against other features.}
 \begin{tabular}{c|c|c|c|c|c}
  \textbf{Feature} & \textbf{LivingRoom} & \textbf{Bedroom} & \textbf{Kitchen} & \textbf{Desk} & \textbf{Average} \\ \hline
  VOP & \textbf{94.57\%} & \textbf{88.31\%} & 82.58\% & \textbf{90.29\%} & \textbf{88.94\%} \\
  $\Delta$ RGB mean & 80\% & 71.84\% & 76.29\% & 73.42\% & 75.39\% \\
  Depth probe& 77.54\% & 61.79\% & \textbf{84.9\%} & 68.9\% & 73.06\% \\
  Color Probe& 56.39\% & 65.68\% & 60.77\% & 60.74\% & 60.9\% \\
  SURF & 43.74\% & 67.12\% & 57\% & 58.13\% & 56.5\% \\
  SPIN & 58.77\% & 43.22\% & 48.41\% & 36.1\% & 46.63\% \\
 \end{tabular}
 \label{fig:vop_results}
\end{table}

>>>>

\begin{table}[!ht]	
 \center
 \caption{Comparison of VOP against other features.}
 \begin{tabular}{c|c|c|c|c|c}
  \textbf{Feature} & \textbf{LivingRoom} & \textbf{Bedroom} & \textbf{Kitchen} & \textbf{Desk} & \textbf{Average} \\ \hline
  VOP & \textbf{94.57\%} & \textbf{88.31\%} & 82.58\% & \textbf{90.29\%} & \textbf{88.94\%} \\
  $\Delta$ RGB mean & 80\% & 71.84\% & 76.29\% & 73.42\% & 75.39\% \\
  Depth Probe& 77.54\% & 61.79\% & \textbf{84.9\%} & 68.9\% & 73.06\% \\
  Color Probe& 56.39\% & 65.68\% & 60.77\% & 60.74\% & 60.9\% \\
  SURF & 43.74\% & 67.12\% & 57\% & 58.13\% & 56.5\% \\
  SPIN & 58.77\% & 43.22\% & 48.41\% & 36.1\% & 46.63\% \\
 \end{tabular}
 \label{fig:vop_results}
\end{table}

### 2015-12-06 cv3d_seminar/presentation.tex
results

\documentclass[mathserif]{beamer}
\input{macro}

@@

@@

@@

@@

%---------------------------------------------------------------------------------------
\section{State of the Art}

\begin{frame}
\frametitle{Another section}
\end{frame}

>>>>

\documentclass[mathserif, 8pt]{beamer}
\input{macro}

% \usepackage[font=footnotesize,labelfont=bf]{caption}
% \setbeamerfont{caption}{size=\scriptsize}

@@

\begin{table}[!ht]
  \fontsize{10pt}{7.2}\selectfont
 \center
 \caption{Segmentation Results}
\noindent\makebox[\linewidth]{
  \begin{tabular}{c|c|c|c|c|c}
    \textbf{Component} & \textbf{LivingRoom} & \textbf{Bedroom} & \textbf{Kitchen} & \textbf{Desk} & \textbf{Average} \\ \hline
    User Interaction & 99.35\% & 97.61\% & 96.09\% & 97.73\% & 97.7\% \\ 
    Forest Prediction & 94.57\% & 88.31\% & 82.58\% & 90.29\% & 88.94\% \\
    Final Inference & 96.26\% & 95.19\% & 90.69\% & 95.55\% & 94.42\%
  \end{tabular}
 }
 \label{fig:segm_results}
\end{table}

@@

\begin{table}[!ht]
 \fontsize{10pt}{7.2}\selectfont
 \center
 \caption{Feature Comparison}
 \noindent\makebox[\linewidth]{
  \begin{tabular}{c|c|c|c|c|c}
  \textbf{Feature} & \textbf{LivingRoom} & \textbf{Bedroom} & \textbf{Kitchen} & \textbf{Desk} & \textbf{Average} \\ \hline
  VOP & \textbf{94.57\%} & \textbf{88.31\%} & 82.58\% & \textbf{90.29\%} & \textbf{88.94\%} \\
  $\Delta$ RGB mean & 80\% & 71.84\% & 76.29\% & 73.42\% & 75.39\% \\
  Depth Probe& 77.54\% & 61.79\% & \textbf{84.9\%} & 68.9\% & 73.06\% \\
  Color Probe& 56.39\% & 65.68\% & 60.77\% & 60.74\% & 60.9\% \\
  SURF & 43.74\% & 67.12\% & 57\% & 58.13\% & 56.5\% \\
  SPIN & 58.77\% & 43.22\% & 48.41\% & 36.1\% & 46.63\% \\
 \end{tabular}
 }
 \label{fig:vop_results}
\end{table}

@@

\begin{columns}
 \begin{column}{0.5\textwidth}
  \begin{figure}[!ht]
  \center
  \includegraphics[width=\textwidth]{figures/srf_ap}
  \vspace{-0.25cm}
  \caption{Average Precision}
  \label{fig:srf_ap}
  \end{figure}
  \vspace{-0.5cm}
  \begin{figure}[!ht]
  \center
  \includegraphics[width=\textwidth]{figures/srf_iu}
  \vspace{-0.25cm}
  \caption{Intersection/Union}
  \label{fig:srf_iu}
  \end{figure}
 \end{column}

 \begin{column}{0.5\textwidth}
  Data:\\
  300 objects\\
  51 classes\\
  full revolution\\
  3 points of view \\
  \vspace{0.5cm}
  SRF - Streaming Random Forest\\
  ORF - Online Random Forest\\
  HT - Hoeffding Tree \\
 \end{column}
\end{columns}

@@
